\LARGE \bf Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-14 09-30-2014]

### 2014-10-02 paper.tex
8 pages

\begin{figure}[ht!]
\centering
\includegraphics[width = 8.5cm, height= 7cm ]{figures/Slide13.jpg}
\caption{Shape samples drawn from Eq. \ref{eq:joint_shape} on the object in the upper left corner. Given a shape sample we highlight the zero-crossing of the level set in black}
\vspace*{-10pt}
\label{fig:shape_samples}
\end{figure}

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width = 17cm, height = 12cm]{figures/Slide09.jpg}
\caption{ \footnotesize Top: Comparison of two sampling methods. Red is the multi-arm bandit method that actively chooses which one to sample and Blue is the naive Monte-Carlo method. We measure their ability to converge in terms of simple regret averaged over 100 runs. We had them determine the best grasp when $|G|=1000$. In all cases the bandit method converges a least a magnitude faster than the pure Monte-Carlo integration. Bottom: Three objects from our data set that we tested on (Tape, Loofa, Water Bottle), we used a visualization technique described in \cite{mahler2015opt}}
\vspace*{-10pt}
\label{fig:simple_regret}
\end{figure*}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=8.5cm,height=9cm]{figures/Slide12.jpg}
\caption{ \footnotesize Time it took to sample from 100 grasp distributions for a given resulution of the workspace. Blue line is sampling from $p(sd(\mathcal{R}))$ or shapes and Red is sampling from $p(g)$ or the calculated distribution on grasps. As you can see sampling from the calculated distributions scales much better. }
\vspace*{-10pt}
\label{fig:speed_dif}
\end{figure}

>>>>

\begin{figure}[ht!]
\centering
\includegraphics[width = 7.5cm, height= 6cm ]{figures/Slide13.jpg}
\caption{Shape samples drawn from Eq. \ref{eq:joint_shape} on the object in the upper left corner. Given a shape sample we highlight the zero-crossing of the level set in black}
\vspace*{-10pt}
\label{fig:shape_samples}
\end{figure}

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width = 14cm, height = 9cm]{figures/Slide09.jpg}
\caption{ \footnotesize Top: Comparison of two sampling methods. Red is the multi-arm bandit method that actively chooses which one to sample and Blue is the naive Monte-Carlo method. We measure their ability to converge in terms of simple regret averaged over 100 runs. We had them determine the best grasp when $|G|=1000$. In all cases the bandit method converges a least a magnitude faster than the pure Monte-Carlo integration. Bottom: Three objects from our data set that we tested on (Tape, Loofa, Water Bottle), we used a visualization technique described in \cite{mahler2015opt}}
\vspace*{-10pt}
\label{fig:simple_regret}
\end{figure*}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=5.7cm,height=6cm]{figures/Slide12.jpg}
\caption{ \footnotesize Time it took to sample from 100 grasp distributions for a given resulution of the workspace. Blue line is sampling from $p(sd(\mathcal{R}))$ or shapes and Red is sampling from $p(g)$ or the calculated distribution on grasps. As you can see sampling from the calculated distributions scales much better. }
\vspace*{-10pt}
\label{fig:speed_dif}
\end{figure}
